Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/introduction.tex
pass on intro -- fleshing out technical details

In contrast, in this paper we present a new method to simultaneously optimize
both network size and model performance. The key idea is to learn the right
network size at the same time that we optimize for prediction performance. Our
approach, called {\it ShrinkNets}, starts with an {\it oversized} network, and
dynamically shrinks it by eliminating neurons during training time.  Our
approach has two main benefits.  First, we explore the architecture of models
that are both small and perform well, rather than starting with a high-
performance model and making it small.  This allows us to efficiently generate
a family of smaller and accurate models without an exhaustive and expensive
hyperparameter search over the number of neurons in each layer. Second, in
contrast to existing neural network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our approach results in models that are
not only small, but where the  layers are dense, which means that inference
time is also improved, e.g., on GPUs.

>>>>

In contrast, in this paper we present a new method to simultaneously optimize
both network size and model performance. The key idea is to learn the right
network size at the same time that we optimize for prediction performance for a
specific task. Our approach, called {\it ShrinkNets}, starts with an {\it
oversized} network, and dynamically shrinks it by eliminating unimportant
neurons---those that do not contribute to prediction performance---during
training time. For that, ShrinkNets must detect the unimportant neurons, and
remove them from the network, thus drastically reducing the network size. The
removal of entire neurons and not connections is crucial, because it leads to
dense networks, which lead to better inference performance. To support the
detection and removal of unimportant neurons we introduce a new layer, called
\textbf{Switch layer}. Introducing this new layer means we must redefine the
loss function to account for the sparsity effect it introduces. ShrinkNets has
two main benefits. First, it explores the architecture of models that are both
small and perform well, rather than starting with a high-performance model and
making it small.  This allows us to efficiently generate a family of smaller and
accurate models without an exhaustive and expensive hyperparameter search over
the number of neurons in each layer.  Second, in contrast to existing neural
network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our
approach results in models that are not only small, but where the layers are
dense, which means that inference time is also improved, e.g., on GPUs.
